Supplementary Information

### 2021-04-08 doc/manuscript/ForestGEO_treerings.Rmd
complete transfer of tables to manuscript, delete old files

\newpage
**Table 1 | (DRAFT hypothesis table-- needs to be filled in and condensed/ cleaned up)**. .... 
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
hypotheses_table <- read.csv("tables_figures/hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypotheses_table <- subset(hypotheses_table, select = -c(table_row, category, notes) )#remove columns that shouldn't be included
ft <- flextable(hypotheses_table)
ft <- autofit(ft)
ft <- footnote( ft, i = 1, j = 2,
                value = as_paragraph(c("SSC= species-site combinations; SSCV=species-site-variable combination")),
                ref_symbols = c("*"),
                part = "header",inline=T)
ft

@@

![ ](tables_figures/hypothesis_table.png)

@@

(*I believe methods can stay mostly the same.*)

@@

**Table 2 | Sites included in this analysis**. Here and throughout, sites are ordered by descending mean annual temperature. Additional site information is provided in Appendix `r site_details_appendix` and Table `r site_details`, and tree species and sampling details are detailed in Tables `r species_table`-`r sampling_details_table`. 
![ ](tables_figures/sites_table.png)

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 8)
sites_table<- read.csv("tables_figures/sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
sites_table <- subset(sites_table, select = -c(MAT, JulyTsd, JanTsd, MAPsd)) #drop MAT column, plus columns with sd
ft <- flextable(sites_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = .5)
ft <- width(ft, 2:3, width = 1)
ft <- width(ft, 4:6, width = .45)
ft <- width(ft, 7, width = .66)
ft <- width(ft, 8, width = .52)
ft <- width(ft, 9, width = .5)
ft <- width(ft, 10, width = 1.5)
ft <- footnote( ft, i = 1, j = 4:6,
                value = as_paragraph(c("Refers to 1950-2019 mean climate.")),
                ref_symbols = c("*"),
                part = "header",inline=T)
ft

>>>>

\newpage
**Table 1 | (DRAFT hypothesis table-- needs to be filled in and condensed/ cleaned up)**. .... 
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
hypotheses_table <- read.csv("tables_figures/hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypotheses_table <- subset(hypotheses_table, select = -c(table_row, Q, H, category, notes) )#remove columns that shouldn't be included
ft <- flextable(hypotheses_table)
ft <- italic(ft, i=c(1,15,21), j=1)
ft <- bold(ft, i=c(1,15,21, 2,6,12,16,22))
ft <- autofit(ft)
ft <- footnote( ft, i = 1, j = 2,
                value = as_paragraph(c("SSC= species-site combinations; SSCV=species-site-variable combination")),
                ref_symbols = c("*"),
                part = "header",inline=T)
ft

@@

@@

@@

\newpage
**Table 2 | Sites included in this analysis**. Here and throughout, sites are ordered by descending mean annual temperature. Additional site information is provided in Appendix `r site_details_appendix` and Table `r site_details`, and tree species and sampling details are detailed in Tables `r species_table`-`r sampling_details_table`. 
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 8)
sites_table<- read.csv("tables_figures/sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
sites_table <- subset(sites_table, select = -c(MAT, JulyTsd, JanTsd, MAPsd)) #drop MAT column, plus columns with sd
ft <- flextable(sites_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = .5)
ft <- width(ft, 2:3, width = 1)
ft <- width(ft, 4:6, width = .45)
ft <- width(ft, 7, width = .66)
ft <- width(ft, 8, width = .52)
ft <- width(ft, 9, width = .5)
ft <- width(ft, 10, width = 1.5)
ft <- footnote( ft, i = 1, j = 4:6,
                value = as_paragraph(c("Refers to 1950-2019 mean climate.")),
                ref_symbols = c("*"),
                part = "header",inline=T)
ft
